---
title: "PSTAT126 Project1"
author: "Bowie Chuang"
date: "2024-04-16"
output: html_document
---

```{r setup, include = FALSE}
# default code chunk options
knitr::opts_chunk$set(echo = F,
                      results = 'markup',
                      message = F, 
                      warning = F,
                      fig.width = 4,
                      fig.height = 3,
                      fig.align = 'center') 

# load packages
library(faraway)
library(tidyverse)
```

# Data Source: Billionaires Statistics Dataset (2023) Kaggle
https://www.kaggle.com/datasets/nelgiriyewithana/billionaires-statistics-dataset/data


```{r, echo = False}
#file.choose()
df = read.csv("/Users/bowiechuang/Downloads/Billionaires Statistics Dataset.csv")
head(df)
```
```{r}
install.packages("skimr")
library(skimr)
```

```{r}
summary <- skim(df)
print(summary)

```

```{r}
set.seed(999)
df1 <- df %>% 
  select(finalWorth, age, country, industries, gender, birthYear, cpi_country, gdp_country,  tax_revenue_country_country, total_tax_rate_country) %>% drop_na()
```

```{r}
summary(df1)
```

```{r}
df1 <- df1[sample(nrow(df1), 500), ]
df1
```

```{r}
install.packages("corrplot")
library(corrplot)
```

```{r}
df1_num <- df1 %>%
  select_if(is.numeric)
correlation_matrix <- cor(df1_num)

corrplot(correlation_matrix, method = "circle", tl.cex = 0.45)

```
Based on the Correlation Matrix, it seems like most of the quantitative variables that we see here are not correlated with one another. This might lead to less correlated results when we dive into linear regression model. 

age and total tax rate, cpi country and total tax rate s

```{r}
ggplot(data = df1, aes(x = age, y = total_tax_rate_country, color = gender))+
  geom_point(alpha = 0.7)+
  geom_smooth(method = 'lm', se = F, color = 'black')+
  labs(x = 'Age', y = 'Total Tax Rate (Country)')

```


```{r}
ggplot(data = df1, aes(x = gender, y = finalWorth)) + geom_boxplot()

```

Indicate population: 

```{r}
library(tidyverse)


hist(df$age)


```
Here is a histogram of the ages of the members when the data was recorded. Although not normal, the data does portray a slightly "bell-curve" look, with the peak being at 55-60 years, and a second peak being around 70 years. This makes statistical sense, since it takes time and experience to accumulate such high amounts of wealth. The graph is also more skewed to the left, and more uniform to the right, which supports this idea even more. It seems like the average age of the members is around 70-80.

```{r}

library(tidyverse)


plot(x = df$life_expectancy_country, y = df$finalWorth )

```





